---
title: "Holyoke Urban Renewal data"
author: "STAT210 and STAT325 classes at Amherst College (Nicholas Horton)"
date: "2024-03-04"
date-format: iso
format: gfm
editor: source
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(HolyokeUrbanRenewal)
```

This file describes the `HolyokeUrbanRenewal` package.
It provides access to archival materials from the Holyoke Public Library History Room Riverview Prospect Heights Urban Renewal Project.

See https://github.com/STAT210-S23/STAT210-Holyoke-History-Room/tree/main/Riverview_Renewal_Project for more information.

The package allows users to explore this archival dataset.

There is a Shiny app (in the `shiny` folder).

The package can be installed by running:

```
devtools::install_github("STAT325-S24/HolyokeUrbanRenewal")
library(HolyokeUrbanRenewal)
```

Because of the size of the package (approximately 1.8GB), it may be necessary to increase the default timeouts:

change: `options(timeout=60)` 

to 

`options(timeout=300)`

This change ensures that the GitHub transaction, which is longer than the default timeout (60 seconds), can complete in time.

If that workaround doesn't succeeed it may be necessary to clone the repo and install from within the RStudio `Build` tab.

```{r}
suppressPackageStartupMessages(library(tidyverse))
citation(package = "HolyokeUrbanRenewal")
glimpse(HolyokeUrbanRenewal)
get_buildings()
```

Kudos to Eileen Crosby, the STAT210 and STAT325 classes at Amherst College, Zoe Jacobs Feinstein, Julia Riseman, and Steffen Plotner for their assistance with this project.

