---
title: "Holyoke Urban Renewal data"
author: "STAT210 and STAT325 class at Amherst College (Nicholas Horton, nhorton@amherst.edu)"
date: "2024-03-03"
date-format: iso
format: gfm
editor: source
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(HolyokeUrbanRenewal)
```

This file describes the `HolyokeUrbanRenewal` package.
It provides access to archival materials from the Holyoke Public Library History Room Riverview Prospect Heights Urban Renewal Project.

See https://github.com/STAT210-S23/STAT210-Holyoke-History-Room/tree/main/Riverview_Renewal_Project for more information.

The package allows users to explore this archival dataset.

There is a Shiny app (in the `shiny` folder).

The package can be installed by running:

```
devtools::install_github("STAT325-S24/HolyokeUrbanRenewal")
library(HolyokeUrbanRenewal)
```

If this doesn't work (due to the size of the images) it may be necessary to clone the repo and install from within the RStudio `Build` tab.

```{r}
suppressPackageStartupMessages(library(tidyverse))
citation(package = "HolyokeUrbanRenewal")
glimpse(HolyokeUrbanRenewal)
get_buildings()
```



