---
title: "Holyoke Urban Renewal data"
author: "STAT325 (Text Analytics) class at Amherst College"
date: "2024-02-26"
date-format: iso
format: gfm
editor: source
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(HolyokeUrbanRenewal)
```

This file describes the `HolyokeUrbanRenewal` package.
It provides access to archival materials from the Holyoke Public Library History Room Riverview Prospect Heights Urban Renewal Project.

See https://github.com/STAT210-S23/STAT210-Holyoke-History-Room/tree/main/Riverview_Renewal_Project for more information.

The package is interesting because it allows users to explore this archival dataset.

The package can be installed by running:

```
devtools::install_github("STAT325-S24/HolyokeUrbanRenewal")
library(HolyokeUrbanRenewal)
```

```{r}
suppressPackageStartupMessages(library(tidyverse))
citation(package = "HolyokeUrbanRenewal")
glimpse(HolyokeUrbanRenewal)
get_filename()
```

Some sample exploration and analyses will be eventually be added here.

